


**Problem Statement** Analysis of the South Africa Heart Disease data using SVM.
```{r,echo=FALSE}
library(ElemStatLearn)
library(e1071)
library(kernlab)
data.train<-SAheart
data.train$chd=as.factor(data.train$chd)
data.train<-data.train[complete.cases(data.train),]

```

**Linear Kernel** For Support vector algorithm we try to find the best model using cross validation. Keeping cost as a varibale changing it from 0.01 to 1000, we find the best model for Linear Kernel. 

```{r,echo=FALSE}
#cross validation by tuning
#linear kernel
set.seed(100)
tune.out=tune(svm,chd~.,data=data.train,
              kernel="linear",ranges=list(cost=c(0.01,0.1,10,100,1000)))
summary(tune.out)
```


**Radial Kernel** For Support vector algorithm we try to find the best model using cross validation. Keeping cost as a varibale changing it from 0.01 to 1000, we find the best model for Radial Kernel. 


```{r,echo=FALSE}
set.seed(100)
#radial kernel
tune.radial.out=tune(svm,chd~.,data=data.train,
              kernel="radial",ranges=list(cost=c(0.01,0.1,10,100,1000)))
summary(tune.radial.out)
```


**Polynomial Kernel** For Support vector algorithm we try to find the best model using cross validation. Keeping cost as a varibale changing it from 0.01 to 1000, we find the best model for Polynomial Kernel. 


```{r,echo=FALSE}
#Polynomial kernel
set.seed(100)
tune.poly.out=tune(svm,chd~.,data=data.train,
              kernel="polynomial",degree = 3, coef0= 1, ranges=list(cost=c(0.01,0.1,10,100,1000)))
summary(tune.poly.out)
```

**RESULT** We find the least error with Polynomial Kernel with 3 degrees and Cost as 0.1. 
